CommonMind Consortium: DLPFC

### 2020-09-22 combined_analysis/diff.networks.Rmd
Update diff networks

df_test_recal = apply_permutation_null( df_test.Sex )

@@

## Module enrichment
```{r top.enrich.Sex}
df_module.Sex = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
						Module = dynamicColors.Sex)

@@

## DE enrichment
```{r cameraPR.Sex}
res_enrich_DE = enrich_module_DE( df_module.Sex )

@@

df_test_recal = apply_permutation_null( df_test.Dx_Sex )

table(df_test_meta$FDR < 0.051)
```

@@

@@

## DE enrichment
```{r cameraPR.Dx_Sex}
res_enrich_DE = enrich_module_DE( df_module.Dx_Sex )

>>>>

df_test_recal.Sex = apply_permutation_null( df_test.Sex )

table(df_test_recal.Sex$FDR < 0.05)

df_test_meta.Sex = module_meta_analysis( df_test_recal.Sex )

table(df_test_meta.Sex$FDR < 0.05)

# plot discovery and testing.      
ggplot(df_test_recal.Sex, aes(Module, -log10(P.Value))) + geom_bar(stat='identity', fill=df_test.Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~P)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed") 
```

```{r plot.meta.Sex}
ggplot(df_test_meta.Sex, aes(Module, -log10(P.Value))) + geom_bar(stat='identity', fill=df_test.Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~P)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")

qqPlot(df_test_meta$P.Value)
```

@@

## Module enrichment
```{r top.enrich.Sex, fig.width=7, fig.height=12}
df_module.Sex = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
						Module = dynamicColors.Sex)

@@

## DE enrichment
```{r cameraPR.Sex, fig.width=7, fig.height=12}
res_enrich_DE = enrich_module_DE( df_module.Sex )

@@

df_test_recal.Dx_Sex = apply_permutation_null( df_test.Dx_Sex )

table(df_test_recal.Dx_Sex$FDR < 0.05)

df_test_meta.Dx_Sex = module_meta_analysis( df_test_recal.Dx_Sex )

table(df_test_meta.Dx_Sex$FDR < 0.051)
```

@@

```{r plot.meta.Dx_Sex}
ggplot(df_test_meta.Dx_Sex, aes(Module, -log10(P.Value))) + geom_bar(stat='identity', fill=df_test.Dx_Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~P)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")

qqPlot(df_test_meta.Dx_Sex$P.Value)
```

@@

## DE enrichment
```{r cameraPR.Dx_Sex, fig.width=7, fig.height=12}
res_enrich_DE = enrich_module_DE( df_module.Dx_Sex )
